---
title: "R02_Prac01_dplyr_ptt"
author: "吳禹辰"
date: "9/25/2019"
output:
  html_document:
    highlight: zenburn
    number_sections: yes
    theme: cerulean
    toc: yes
    css: style.css
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading pkgs and options
```{r}
# add essential pkgs here
library(tidyverse)
options(stringsAsFactors = F)
```


# Loading rda data
- will creating two data frames, `posts` and `comments`.
```{r}
load("data/HatePolitics_Hang_20190101_2019_06_01.rda")

```


# Counting the top 5 commentors
- 找出回文數最高的五個人
```{r}
comments %>%
  count(commentor) %>%
  arrange(desc(n)) %>%
    slice(1:5)
```


# Counting the top 5 posters
- 找出發文數最高的五個人
```{r}
posts %>%
    count(poster) %>%
  arrange(desc(n)) %>%
    slice(1:5)
```


# Enumerating comment order for each posts
- 產生兩個新的變項，`cindex`指出該則回文為該篇貼文的第幾則回文，`ctotal`指出該則回文所在的貼文共有幾則回文。
- enumerating the order, the "floor", of each comment
- Who are always reponse to Hang's posts very soon?
- Practice goal: Using `group_by` and `mutate()`
- comment order should be `cindex`
- total comments of a post should be `ctotal`
- You must use `row_number()` to get the order of each comment.
```{r}
comments %>%
    group_by(plink) %>%
  mutate(cindex = row_number()) %>%
  mutate(ctotal = max(cindex)) %>%
  ungroup() %>%
    select(tag, commentor, cindex, ctotal) %>%
    head(n=20)
```

# Calculating the average response order for each commentor
- 延續上題，計算出每一個人回應的平均樓層（`avg_order` 比方說，某人共在三篇貼文的回應樓層為第3樓、第6、第9樓，其平均回應樓層為6）；如果除以該則貼文的總回文樹的話，就會變成平均回文樓層比例（以下範例為有除以總回文數的結果）。另外順便計算標準差（`sd_order`）以及每個人的總回文數量`tot_comment`。
- Filter out those posts with fewer than 5 comments 不列計少於5則回文的貼文
- Filter out those commentors with fewer than 10 comments 不列計在資料中回文總數少於10則的回文者
- Only show top 10 commentors who always respond very fast

```{r}
comments %>%
  group_by(plink) %>%
  mutate(cindex = row_number()) %>%
  mutate(ctotal = max(cindex)) %>%
  ungroup() %>%
  filter(ctotal >= 5) %>%
  group_by(commentor) %>%
  mutate(num = 1) %>%
  summarise(avg_order = mean(cindex/ctotal), sd_order = sd(cindex/ctotal), tot_comment = sum(num) ) %>%
  filter(tot_comment >= 10) %>%
  arrange(avg_order) %>%
    slice(1:10)
```

# Challenge: Counting how many posts each commentor has responded to 
針對每一個回文者，計算出下列數值
1. 一共回過多少則post，一個post多個回文仍只算一次
2. 針對每篇post，最多曾回應一篇post幾次
3. 針對每篇post，最少曾回應一篇post幾次
4. 針對每篇post，平均回應過幾次
5. 針對每篇post，回應次數的標準差
```{r}
comments %>%
  group_by(commentor,plink) %>%
    summarise(com_in1 = length(plink)) %>%
  group_by(commentor) %>%
    summarise(num_post = length(com_in1),max_c2p = max(com_in1) , min_c2p = min(com_in1) , mean_c2p = mean(com_in1) , sd_c2p = sd(com_in1)) %>%
    arrange(desc(num_post)) %>%
    slice(1:30)
```

# Call for idea
- Except the above methods, try to propose your idea to show questionable users, possible big fans, and high frequency enthusiasts.

```{r}
comments %>% 
  filter(commentor %in% c("jma306", "ckbdfrst" , "popy8789" , "flavorBZ",
"wangyc"               )) %>%
  select(commentor , ccontent) %>%
  arrange(commentor)
#觀察回文速度最快的幾個人，可以發現其中許多都是相當熱衷討論政治且立場明確的人
#如ckbdfrst相當反韓，而flavorBZ, wangyz則非常偏藍

comments %>% 
  filter(commentor %in% c(  "aylao","bottger" ,"gn02118620","ninaman", "zeumax" )) %>%
  select(commentor , ccontent) %>%
  arrange(commentor)
#而觀察回過的post最多的用戶，可以發現前五名幾乎都是「韓粉」，相當可疑
```

