---
title: "R Notebook"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##import

```{r}
library(tidyverse)
library(tidytext)
options(stringsAsFactors = F)
```

```{r}
sample_sheet <- read_csv("data/hackathon/task1_sample_submission.csv")
sample_sheet %>% head %>% View
```

# 01 Loading data
- Mutate sentence_id
- Segmenting text to sentence



## Cleaning test set
- Sentence_id must be given separated from training set. Because sentences of docs in training set may have multiple labels but with the sample sentence_id.

```{r}
# 20000 abstract in testing data
raw.test <- read_csv("data/hackathon/task1_public_testset.csv") %>% 
    mutate(sentence  = str_split(Abstract, "\\$+")) %>%
    unnest(sentence) %>%
    mutate(index = FALSE) %>% 
    select(-Abstract) %>%
    select(doc_id = Id, everything()) %>%
    group_by(doc_id) %>%
    mutate(sentence_id = str_c(doc_id, "_S", str_pad(row_number(), 3, pad="0"))) %>%
    mutate(sentence_perc = row_number()/n()) %>%
    ungroup()
    
```


## Cleaning training set
- Unnest sentence and sentence types
- Labeling sentences with sentence_id

```{r}
raw_1 <- read_csv("data/hackathon/task1_trainset.csv") %>%
    mutate(sentence  = str_split(Abstract, "\\$+"),
           sentence_type = str_split(`Task 1`, " ")) %>%
    unnest(sentence, sentence_type) %>%
    mutate(index = TRUE) %>%
    select(doc_id = Id, everything()) %>%
    group_by(doc_id) %>%
    mutate(sentence_id = str_c(doc_id, "_S", str_pad(row_number(), 3, pad="0"))) %>%
    mutate(sentence_perc = row_number()/n()) %>%
    ungroup() %>%
    select(-`Task 1`, -Abstract)
```

## Combining training and test sets
- Unnesting sentences with multiple labels
- Merging all training sentences data
- Creating dependent variables to multiple columns
- Merging test set

```{r}
raw <- raw_1 %>%
    filter(str_detect(sentence_type, "/")) %>%
    mutate(sentence_type = str_split(sentence_type, "/"))%>%
    unnest(sentence_type) %>%
    bind_rows(raw_1 %>% filter(!str_detect(sentence_type, "/"))) %>%
    mutate(value = 1) %>%
    spread(sentence_type, value, fill = 0) %>%
    bind_rows(raw.test)
```




# 03 Word Feature selections

## 3.1 stop_words as features

```{r}
doc_word_count <- raw %>%
    select(sentence_id, sentence) %>%
    unnest_tokens(word, sentence, token = "regex", pattern = "[^A-Za-z\\d#@']") %>%
    filter(word %in% stop_words$word) %>%
    group_by(word) %>%
    filter(n() > 20) %>%
    ungroup() %>%
    filter(!word %in% c("in", "a", "to", "and", "for", "that", "is", "on", "with", "are", "by", "an", "be")) %>%
    count(sentence_id, word) %>%
    bind_tf_idf(word, sentence_id, n)


message("Number of words: ", unique(doc_word_count$word) %>% length)
```





#Building dtm
```{r}

dtm <- doc_word_count %>% 
    cast_dtm(document = sentence_id, term = word, value = tf)

# dtm %>% dim
# dtm %>% as.matrix() %>% as_data_frame() %>% head(20) %>% View


mat.df <- dtm %>% as.matrix() %>% as_tibble() %>%
    bind_cols(sentence_id = dtm$dimnames$Docs) %>%
    right_join(raw %>% select(sentence_id,  index, sentence_perc, sentence_type = BACKGROUND))
colnames(mat.df) <- make.names(colnames(mat.df))
```

###首先測試模型，先以train.df中的資料進行train與test，取70% train，30% test

```{r}
test <- mat.df[mat.df$index, ] %>%
    drop_na()

index <- sample(1:nrow(test), ceiling(nrow(test) * .70))

train.df <- test[index, ]
test.df <- test[-index, ]
test.df[is.na(test.df)] <- 0


dim(train.df)
dim(test.df)
```

#在以單一變數的情況下準確度高達98.28931%

```{r}
library(glmnet)

predicted <- test.df %>%
    select(sentence_id, sentence_type)

stime <- Sys.time()
glm.fit <- glmnet(train.df %>% select(-sentence_type, -sentence_id) %>% as.matrix(), 
                  as.factor(train.df$sentence_type), 
                  family = 'binomial')
Sys.time() - stime


predicted$mnl <- predict(glm.fit, 
                       test.df %>% select(-sentence_id, -sentence_type) %>% as.matrix(), 
                       s = 0.0025, type = "class") 



(conf.mat <- table(predicted$mnl, predicted$sentence_type))
(accuracy <- sum(diag(conf.mat))/sum(conf.mat) * 100)

```



###將所有training資料用做training，並預測hackathon的資料集
```{r}
train.df <- mat.df[mat.df$index, ] %>%
    drop_na()
test.df <- mat.df[!mat.df$index, ]
test.df[is.na(test.df)] <- 0


dim(train.df)
dim(test.df)
```


# 07 Modeling


## 使用binomial的方法並用glmnet做預測哪些句子為BACKGROUND

```{r}
library(glmnet)

stime <- Sys.time()
glm.fit <- glmnet(train.df %>% select(-sentence_type, -sentence_id) %>% as.matrix(), 
                  as.factor(train.df$sentence_type), 
                  family = 'binomial')
Sys.time() - stime


predicted.df <- predict(glm.fit, 
                       test.df %>% select(-sentence_id, -sentence_type) %>% as.matrix(), 
                       s = 0.0025, type = "class") %>%  
    as.data.frame() %>%
    bind_cols(test.df %>% 
                  select(sentence_id)) %>%
    select(sentence_id,
           BACKGROUND=`1`)

result.df <- predicted.df 

```

```{r}

  mat.df <- dtm %>% as.matrix() %>% as_tibble() %>%
      bind_cols(sentence_id = dtm$dimnames$Docs) %>%
      right_join(raw %>% select(sentence_id,  index, sentence_perc, sentence_type = OBJECTIVES))
  colnames(mat.df) <- make.names(colnames(mat.df))

  
  train.df <- mat.df[mat.df$index, ] %>%
      drop_na()
  test.df <- mat.df[!mat.df$index, ]
  test.df[is.na(test.df)] <- 0
  
  
  dim(train.df)
  dim(test.df)

  stime <- Sys.time()
  glm.fit <- glmnet(train.df %>% select(-sentence_type, -sentence_id) %>% as.matrix(), 
                    as.factor(train.df$sentence_type), 
                    family = 'binomial')
  Sys.time() - stime
  
  
  predicted.df <- predict(glm.fit, 
                         test.df %>% select(-sentence_id, -sentence_type) %>% as.matrix(), 
                         s = 0.0025, type = "class") %>%  
      as.data.frame() %>%
      bind_cols(test.df %>% 
                    select(sentence_id)) %>%
      select(sentence_id,
             OBJECTIVES=`1`)
  
  result.df <- bind_cols(result.df, OBJECTIVES = predicted.df$OBJECTIVES)
  result.df

```

```{r}
  mat.df <- dtm %>% as.matrix() %>% as_tibble() %>%
      bind_cols(sentence_id = dtm$dimnames$Docs) %>%
      right_join(raw %>% select(sentence_id,  index, sentence_perc, sentence_type = METHODS))
  colnames(mat.df) <- make.names(colnames(mat.df))

  
  train.df <- mat.df[mat.df$index, ] %>%
      drop_na()
  test.df <- mat.df[!mat.df$index, ]
  test.df[is.na(test.df)] <- 0
  
  
  dim(train.df)
  dim(test.df)

  stime <- Sys.time()
  glm.fit <- glmnet(train.df %>% select(-sentence_type, -sentence_id) %>% as.matrix(), 
                    as.factor(train.df$sentence_type), 
                    family = 'binomial')
  Sys.time() - stime
  
  
  predicted.df <- predict(glm.fit, 
                         test.df %>% select(-sentence_id, -sentence_type) %>% as.matrix(), 
                         s = 0.0025, type = "class") %>%  
      as.data.frame() %>%
      bind_cols(test.df %>% 
                    select(sentence_id)) %>%
      select(sentence_id,
             METHODS=`1`)
  
  result.df <- bind_cols(result.df, METHODS = predicted.df$METHODS)
  result.df
```

```{r}
  mat.df <- dtm %>% as.matrix() %>% as_tibble() %>%
      bind_cols(sentence_id = dtm$dimnames$Docs) %>%
      right_join(raw %>% select(sentence_id,  index, sentence_perc, sentence_type = RESULTS))
  colnames(mat.df) <- make.names(colnames(mat.df))

  
  train.df <- mat.df[mat.df$index, ] %>%
      drop_na()
  test.df <- mat.df[!mat.df$index, ]
  test.df[is.na(test.df)] <- 0
  
  
  dim(train.df)
  dim(test.df)

  stime <- Sys.time()
  glm.fit <- glmnet(train.df %>% select(-sentence_type, -sentence_id) %>% as.matrix(), 
                    as.factor(train.df$sentence_type), 
                    family = 'binomial')
  Sys.time() - stime
  
  
  predicted.df <- predict(glm.fit, 
                         test.df %>% select(-sentence_id, -sentence_type) %>% as.matrix(), 
                         s = 0.0025, type = "class") %>%  
      as.data.frame() %>%
      bind_cols(test.df %>% 
                    select(sentence_id)) %>%
      select(sentence_id,
             RESULTS=`1`)
  
  result.df <- bind_cols(result.df, RESULTS = predicted.df$RESULTS)
  result.df
```
  
```{r}
  mat.df <- dtm %>% as.matrix() %>% as_tibble() %>%
      bind_cols(sentence_id = dtm$dimnames$Docs) %>%
      right_join(raw %>% select(sentence_id,  index, sentence_perc, sentence_type = CONCLUSIONS))
  colnames(mat.df) <- make.names(colnames(mat.df))

  
  train.df <- mat.df[mat.df$index, ] %>%
      drop_na()
  test.df <- mat.df[!mat.df$index, ]
  test.df[is.na(test.df)] <- 0
  
  
  dim(train.df)
  dim(test.df)

  stime <- Sys.time()
  glm.fit <- glmnet(train.df %>% select(-sentence_type, -sentence_id) %>% as.matrix(), 
                    as.factor(train.df$sentence_type), 
                    family = 'binomial')
  Sys.time() - stime
  
  
  predicted.df <- predict(glm.fit, 
                         test.df %>% select(-sentence_id, -sentence_type) %>% as.matrix(), 
                         s = 0.0025, type = "class") %>%  
      as.data.frame() %>%
      bind_cols(test.df %>% 
                    select(sentence_id)) %>%
      select(sentence_id,
             CONCLUSIONS=`1`)
  
  result.df <- bind_cols(result.df, CONCLUSIONS = predicted.df$CONCLUSIONS)
  result.df
```



```{r}
  mat.df <- dtm %>% as.matrix() %>% as_tibble() %>%
      bind_cols(sentence_id = dtm$dimnames$Docs) %>%
      right_join(raw %>% select(sentence_id,  index, sentence_perc, sentence_type = OTHERS))
  colnames(mat.df) <- make.names(colnames(mat.df))

  
  train.df <- mat.df[mat.df$index, ] %>%
      drop_na()
  test.df <- mat.df[!mat.df$index, ]
  test.df[is.na(test.df)] <- 0
  
  
  dim(train.df)
  dim(test.df)

  stime <- Sys.time()
  glm.fit <- glmnet(train.df %>% select(-sentence_type, -sentence_id) %>% as.matrix(), 
                    as.factor(train.df$sentence_type), 
                    family = 'binomial')
  Sys.time() - stime
  
  
  predicted.df <- predict(glm.fit, 
                         test.df %>% select(-sentence_id, -sentence_type) %>% as.matrix(), 
                         s = 0.0025, type = "class") %>%  
      as.data.frame() %>%
      bind_cols(test.df %>% 
                    select(sentence_id)) %>%
      select(sentence_id,
             OTHERS=`1`)
  
  result.df <- bind_cols(result.df, OTHERS = predicted.df$OTHERS)
  result.df
```

###依序做完六種sentence type後，整理資料並輸出

```{r}

result.df <- result.df %>% rename(order_id = sentence_id) 
result.df %>% write_csv("./data/hackathon/result.csv")
```


```{r}
result.df <- result.df %>% mutate(BACKGROUND = as.numeric(BACKGROUND), OBJECTIVES = as.numeric(OBJECTIVES), METHODS = as.numeric(METHODS), RESULTS = as.numeric(RESULTS), CONCLUSIONS = as.numeric(CONCLUSIONS), OTHERS = as.numeric(OTHERS))
result <- bind_rows(result.df, sample_sheet %>% slice(131167:262948))
result %>% write_csv("./data/hackathon/result.csv")
```


